Verification of concurrent design patterns with data

### 2019-02-15 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper (Minor): update to the defintion of the export function in Def 10 (Application of an architecture)
arch-pNets paper (Minor): update to the defintion of the export function in Def 10 (Application of an architecture) - reduced the size of parentheses
Quelques refs biblio

The methodology we propose is thus to an encoding of BIP architectures into open pNet in order to be able to verify, using SMT techniques, the coordination capabilities of the architecture, and more generally its properties. The encoding will also give us feedback on the comparison between the BIP architectures and the pNet formalism. 
Overall, the encoding allows us to precisely compare the coordination mechanisms of the two models but also the way component composition is expressed in the two formalisms. This article is also the opportunity to investigate further on  compositional verification by relating two different composition mechanisms that provide different vision on compositional verification. \noteLH{pas tres heureux la fin: pas assez detaille ou trop complique -> abstraire ou detailller a mon avis (Ludo)}\noteEM{j'ai prefere abstraire...}

\paragraph{Contributions}

@@

For a component $B$, we denote $S_{\semopen{B}}$ and
$s^0_{\semopen{B}}$ the corresponding constituents of
$\semopen{B}$ (see Definition~\ref{defn:comp:semantics}).

@@

>>>>

The methodology we propose is thus to an encoding of BIP architectures
into open pNet in order to be able to verify, using SMT techniques,
the coordination capabilities of the architecture, and more generally
its properties. The encoding will also give us feedback on the
comparison between the BIP architectures and the pNet formalism.  
Overall, the encoding allows us to precisely compare the coordination
mechanisms of the two models but also the way component composition is
expressed in the two formalisms. This article is also the opportunity
to
% investigate further on  compositional verification by
relate two different composition mechanisms that provide different
vision on compositional verification. \noteLH{pas tres heureux la fin:
  pas assez detaille ou trop complique -> abstraire ou detailller a
  mon avis (Ludo). J'ai prefere abstraire/raccourcir... (Eric)}

\paragraph{Contributions}
The main contributions of this paper are: 1) The definition of a
theory of BIP architectures with data, including a theorem about
preservation of (data dependent) properties by architecture
compositions. 2) An encoding of architectures with data into the open pNet
model, allowing for analysis of their temporal properties using pNet's
software tools.

@@

For a component $B$, we denote $S_{\semopen{B}}$ and
$s^0_{\semopen{B}}$ the corresponding constituents of
$\semopen{B}$.

@@

various classe infinite-state systems and/or paramaterized topologies
via predicate abstraction and SMT satisfiability:
\cite{DBLP:conf/cade/GhilardiNRZ08,DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}
